Test Maps

### 2021-07-14 Solent Mapping_v2.Rmd
fixed heading structure

## Mapping the Local Authority

### Mapping Domestic

#### Mapping Electricity Consumption

@@

### Mapping Transport

@@

## Mapping the Middle Layer Super Output Areas (MSOA)

### Mapping Domestic

#### Mapping the Electricity Consumption

@@

#### Mapping the Gas
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

### Mapping Commercial
#### Mapping Electricty
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
#### Mapping Gas

@@

## Mapping the Lower Layer Super Output Area (LSOA)

### Mapping Domestic

#### Mapping Electricity consumption
```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
lsoa_elecData <- readr::read_csv(inFile)
lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
head(msoa_elecData)
```

@@

##### Looking at cities in more detail
```{r Looking at the cities in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

@@

#### Mapping Gas

@@

### Mapping Industrial
#### Mapping Electricity consumption

> didn't we already do this in the MSOA section?

```{r Loading in the LSOA electricity consumption data for industry }
# electricity consumption data for industry at LSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

### Mapping the Indices of Multiple Deprivation

>>>>

# Mapping the Local Authority

## Mapping Domestic Electricity Consumption

@@

## Mapping Transport

@@

# Mapping the Middle Layer Super Output Areas (MSOA)

## Mapping Domestic

### Mapping the Electricity Consumption

@@

### Mapping the Gas
```{r Loading in the MSOA gas consumption data}
# gas consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
msoa_gasData <- readr::read_csv(inFile)
head(msoa_gasData)
```
```{r Mapping the gas consumption of the MSOAs}
msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
ggplot2::ggplot(msoa_merged_sf_domgas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
> Does this match to non-gas areas??

## Mapping Commercial
### Mapping Electricty
```{r Loading in the MSOA electricity consumption data for industry }
# electricity consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
msoa_elecDatanondom <- readr::read_csv(inFile)
head(msoa_elecDatanondom)
```

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
### Mapping Gas

@@

# Mapping the Lower Layer Super Output Area (LSOA)

## Mapping Domestic

### Mapping Electricity consumption
```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
lsoa_elecData <- readr::read_csv(inFile)
lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
head(msoa_elecData)
```

@@

#### Looking at cities in more detail
```{r Looking at the cities in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

@@

### Mapping Gas

@@

## Mapping the Indices of Multiple Deprivation
